Relict deciduous oaks show high resilience to drought despite the effect of land-use legacies

### 2019-08-12 man/figures/ring_climate.Rmd
change colors and scale

library("grid")
library("gridExtra")
library("patchwork")
library("ggcorrplot")
library("stringr")
library("pander")
library("lemon")
```

@@

```{r plot_options}
theme_ring_climate <- list(
  geom_hline(yintercept = 0, colour="gray"), 
  geom_bar(aes(fill=site), stat="identity", position = position_dodge2(padding = 0.1)),
  geom_text(aes(label = sig, x = id, y = ifelse(coef > 0, (coef + 0.02), (coef - 0.06))), 
            position = position_dodge(.9), size = 3), 
  theme_bw() +
  theme(axis.title.x = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor.y = element_blank(),
        panel.grid.minor.x = element_line(size=.5),
        axis.text.x.top = element_text(angle = 90, hjust = 0, vjust = 0.5, size = 7),
        axis.text.x.bottom = element_text(angle = 90, hjust = 1, vjust = 0.5, size = 7),
        axis.text.y = element_text(size = 7), 
        axis.title.y = element_text(size = 8),
        legend.text = element_text(size = 7), 
        legend.box.spacing = unit(0.01, "cm")),
  scale_fill_manual(values = c("#B2DF8A","#1F78B4","#A6CEE3"), labels = label_site)
) 
```

```{r plot_tmax}
p_tmax <- df %>% filter(v_name == 'T max') %>% 
  ggplot(aes(x=id, y=coef, group = site)) + 
  theme_ring_climate + 
  scale_y_continuous(limits = c(-0.4, 0.4), 
                     breaks = c(-0.4, -0.2, 0, 0.2, 0.4), 
                     sec.axis = dup_axis(name = NULL)) +
  scale_x_continuous(breaks = unique(df$id), labels = unique(df$month_name), position = 'bottom') + 
  ylab('Correlation') + 
  annotate("text", x = 2, y = 0.35, label = "T max", fontface =2, size = 3.5)
```

```{r plot_tmin}
p_tmin <- df %>% filter(v_name == 'T min') %>% 
  ggplot(aes(x=id, y=coef, group = site)) + 
  theme_ring_climate + 
  scale_y_continuous(limits = c(-0.4, 0.4), 
                     breaks = c(-0.4, -0.2, 0, 0.2, 0.4), 
                     sec.axis = dup_axis(name = NULL)) +
  scale_x_continuous(breaks = unique(df$id), labels = unique(df$month_name), position = 'top') + 
  ylab('Correlation') +
  annotate("text", x = 2, y = 0.35, label = "T min", fontface =2, size = 3.5)
```

@@

p_prec_spei <- dfprec_spei %>% 
  ggplot(aes(x=id, y=coef, group = site)) + 
  geom_vline(xintercept=20) +
  theme_ring_climate + 
  scale_y_continuous(limits = c(-0.2, 0.8), 
                     breaks = c(-0.2, 0, 0.2, 0.4, 0.6, 0.8), 
                     sec.axis = dup_axis(name = NULL)) +
  scale_x_continuous(breaks = labelitas$id, labels = labelitas$month_name, position = 'top') + 
  ylab('Correlation') +
  annotate("text", x = 2, y = 0.75, label = "Prec", fontface =2, size = 3.5) + 
  annotate("text", x = 23, y = 0.75, label = "SPEI", fontface =2, size = 3.5)
```

>>>>

library("grid")
library("gridExtra")
library("patchwork")
library("ggcorrplot")
library("stringr")
library("pander")
library("lemon")
source(here::here('/script/R/colores_den.R'))
```

@@

```{r plot_options}
theme_ring_climate <- list(
  geom_hline(yintercept = 0, colour="gray"), 
  geom_bar(aes(fill=site), stat="identity", position = position_dodge2(padding = 0.1)),
  geom_text(aes(label = sig, x = id, y = ifelse(coef > 0, (coef + 0.02), (coef - 0.06))), 
            position = position_dodge(.9), size = 3), 
  theme_bw() +
  theme(axis.title.x = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor.y = element_blank(),
        panel.grid.minor.x = element_line(size=.5),
        axis.text.x.top = element_text(angle = 90, hjust = 0, vjust = 0.5, size = 7),
        axis.text.x.bottom = element_text(angle = 90, hjust = 1, vjust = 0.5, size = 7),
        axis.text.y = element_text(size = 7), 
        axis.title.y = element_text(size = 8),
        legend.text = element_text(size = 7), 
        legend.box.spacing = unit(0.01, "cm")),
  scale_fill_manual(values = colores_den, labels = label_site)
) 
#c("#B2DF8A","#1F78B4","#A6CEE3")
```

```{r plot_tmax}
p_tmax <- df %>% filter(v_name == 'T max') %>% 
  ggplot(aes(x=id, y=coef, group = site)) + 
  theme_ring_climate + 
scale_y_continuous(limits = c(-0.4, 0.8), 
                     breaks = c(-0.4, -0.2, 0, 0.2, 0.4, 0.6, 0.8), 
                     sec.axis = dup_axis(name = NULL)) +
  scale_x_continuous(breaks = unique(df$id), labels = unique(df$month_name), position = 'bottom') + 
  ylab('Correlation') + 
  annotate("text", x = 2, y = 0.35, label = "T max", fontface =2, size = 3.5)
```

```{r plot_tmin}
p_tmin <- df %>% filter(v_name == 'T min') %>% 
  ggplot(aes(x=id, y=coef, group = site)) + 
  theme_ring_climate + 
  scale_y_continuous(limits = c(-0.4, 0.8), 
                     breaks = c(-0.4, -0.2, 0, 0.2, 0.4, 0.6, 0.8), 
                     sec.axis = dup_axis(name = NULL)) +
  scale_x_continuous(breaks = unique(df$id), labels = unique(df$month_name), position = 'top') + 
  ylab('Correlation') +
  annotate("text", x = 2, y = 0.35, label = "T min", fontface =2, size = 3.5)
```

@@

p_prec_spei <- dfprec_spei %>% 
  ggplot(aes(x=id, y=coef, group = site)) + 
  geom_vline(xintercept=20) +
  theme_ring_climate + 
  scale_y_continuous(limits = c(-0.4, 0.8), 
                     breaks = c(-0.4, -0.2, 0, 0.2, 0.4, 0.6, 0.8), 
                     sec.axis = dup_axis(name = NULL)) +
  scale_x_continuous(breaks = labelitas$id, labels = labelitas$month_name, position = 'top') + 
  ylab('Correlation') +
  annotate("text", x = 2, y = 0.75, label = "Prec", fontface =2, size = 3.5) + 
  annotate("text", x = 23, y = 0.75, label = "SPEI", fontface =2, size = 3.5)
```
